Wireframe2DOM: From Static Graph to Responsive HTML

### 2020-05-01 document/paper.tex

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\section{Illustrative example}
% Shangyin
\section{Background}
% Shangyin
\section{Formal problem definition}
% Shangyin
\section{Algorithm}
% Shangyin
\subsection{Workflow}
Static Graph (the absolute location of each component) $=>$ relative intermediate representation $=>$HTML
\subsection{Grammar}
\subsubsection{Input}
RECT\\
RECTLIST:= RECTLIST RECT | Nil
\subsubsection{IR}
DIV\\
HDIV:= HDIV|DIV|VDIV\\
VDIV:= HDIV|DIV|VDIV\\
First we divide the rectangles into section based on their $y$-axis. Then we use
greedy to find the earliest possible cut $y$ such that this $y$ does not divide any
other rects.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{wrapfig}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\section{Illustrative example}
% Shangyin
\section{Formal problem definition}
% Shangyin
In program synthesis setting, 
\section{Preliminaries}
% Shangyin
\subsection{Workflow}
\begin{wrapfigure}{r}{0.25\textwidth}
  \vspace*{-0.5in}
  \includegraphics[width=0.25\textwidth]{src/workflow.JPG}
\end{wrapfigure}
We define our workflow as a two-staged program. In the first stage, we synthesize the input Wireframe rectangles to IR. Then IR is compiled into universal HTML compatible with any browser in the second stage.

\subsection{IR Definition}

\section{Algorithm}
% Shangyin
In this section, we explain the procedures we used synthesizing the list of rectangles to IR with an estimate order of time complexity. We also present the compilation process from IR to final HTML result.
\subsection{IR Synthesis}
Recall that the input is a list of rectangles. This is the starting point of the synthesis, and we target the nested hierarchical IR. 
\subsubsection{Cut}

\subsubsection{Input}
RECT\\
RECTLIST:= RECTLIST RECT | Nil
\subsubsection{IR}
DIV\\
HDIV:= HDIV|DIV|VDIV\\
VDIV:= HDIV|DIV|VDIV\\
First we divide the rectangles into section based on their $y$-axis. Then we use
greedy to find the earliest possible cut $y$ such that this $y$ does not divide any
other rects.
